\documentclass[]{article}
\usepackage{fullpage}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{textcomp}
\usepackage{hyperref}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[margin=1in]{geometry}
\textheight=10in
\pagestyle{empty}
\raggedright

%\renewcommand{\encodingdefault}{cg}
%\renewcommand{\rmdefault}{lgrcmr}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

% DEFINITIONS FOR RESUME %%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\area} [2] {
	\vspace*{-9pt}
	\begin{verse}
		\textbf{#1}   #2
	\end{verse}
}

\newcommand{\lineunder} {
	\vspace*{-8pt} \\
	\hspace*{-18pt} \hrulefill \\
}

\newcommand{\header} [1] {
	{\hspace*{-18pt}\vspace*{6pt} \textsc{#1}}
	\vspace*{-6pt} \lineunder
}

\newcommand{\employer} [3] {
	{ \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }
}

\newcommand{\contact} [3] {
	\vspace*{-10pt}
	\begin{center}
		{\Huge \scshape {#1}}\\
		#2 \\ #3
	\end{center}
	\vspace*{-8pt}
}

\newenvironment{achievements}{
	\begin{list}
		{$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}
	\end{list}
}

\newcommand{\schoolwithcourses} [4] {
	\textbf{#1} #2 $\bullet$ #3\\
	#4 \\
	\vspace*{5pt}
}

\newcommand{\school} [4] {
	\textbf{#1} #2 $\bullet$ #3\\
	#4 \\
}
% END RESUME DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
	\vspace*{-40pt}
	
	
	%==== Profile ====% 
	\vspace*{-10pt}
	\begin{center}
		{\Huge \scshape {Tyler W. Carson}}\\
		$\ $San Jose, CA $\ \cdot\ $ tyler.w.carson@gmail.com $\ \cdot\ $ (909) 756-5942\\ linkedin.com/in/twcarson $\ \cdot\ $ github.com/yzgncx $\ \cdot\ $ inaturalist.org/people/t-w-carson\\
	\end{center}
	
	
	%==== Work Experience ====%
	\header{Work Experience}
	\vspace{1mm}

	\textbf{Sensory, Inc.} \hfill Portland, OR (remote)\\
	\textit{Product Linguist} \hfill May 2023 - May 2025\\
	\vspace{-3mm}
	\begin{itemize} \itemsep 0pt
		\item Created, documented, and maintained internal software tools written in Python and Bash.
		\item Trained and tested artificial neural networks built for wake word and command recognition, for major automotive and consumer electronics companies.
		\item Applied linguistic and phonetic expertise and research methods to analyze speech spectrograms and curate audio datasets.
		\item Used research methods to find optimal model parameters and best practices for data curation.
		\item Balanced the work of several simultaneous projects with tight deadlines.
	\end{itemize}

	
	\textbf{SoundHound, Inc.} \hfill Santa Clara, CA\\
	\textit{Linguistic Engineer} \hfill Aug 2021 - Jan 2023\\
	\vspace{-3mm}
	\begin{itemize} \itemsep 0pt
		\item Created experimental and production acoustic models for several languages, often delivering models on tight time-frames.  Produced scripts to automate and streamline multi-step training processes.
		\item Lead meetings and coordinated presentations for a team of engineers and linguists.
		\item Worked in a small team to port a legacy repository from C to Python. 
	\end{itemize}
	\vspace{-2mm}
	\textit{Language Data Specialist} \hfill Mar 2020 - Aug 2021\\
	\vspace{-3mm}
	\begin{itemize} \itemsep 0pt
		\item Trained and debugged acoustic models and language models for automatic speech recognition.  
		\item Developed and iterated on a web tool for audio data collection written in Javascript \& HTML.
		\item Designed, set up, and maintained a MySQL database for cataloging text and audio data used in creating text to speech models.
	\end{itemize}
	\vspace{-2mm}
	\textit{English Data Intern} \hfill Aug 2019 - Mar 2020\\
	\vspace{-3mm}
	\begin{itemize} \itemsep 0pt
		\item Organized and lead scripting lessons and office hours for other interns and team members.
		\item Developed a collection of tools in Python for scraping and conditioning text data for use in a linguistic corpus.
	\end{itemize}
	
	\textbf{The Belrose at The Renaissance Pleasure Faire} \hfill Irwindale, CA\\
	\textit{Costume Rental Shop Manager} \hfill 2019 - Present (seasonal)\\
	\vspace{-3mm}
	\begin{itemize} \itemsep 0pt
		\item Manage hiring, training, scheduling and payroll for a business of 20 employees.
		\item Maintain detailed reports of transations, revenue, and expenses.
		\item Implement data-driven approaches to increase business revenues.
		\item Create shop protocols and process improvements, soliciting the input of team members. 
	\end{itemize}
	\vspace{1mm}
	
	\textbf{UCLA Linguistics} \hfill Los Angeles, CA\\
	\textit{Undergraduate Researcher} \hfill Jul 2017 - Oct 2018\\
	\vspace{-3mm}
	\begin{itemize} \itemsep 0pt
		\item Developed software in OCaml for calculating the complexity of grammar in natural language sentences using concepts based in information-theory.
		\item Contributed code for calculating the entropy of a probabilistic formal grammar.
	\end{itemize}
	
	\header{Projects}
	{\textbf{Analysis of Uyghur Vowel Harmony}} \hspace*{5mm} {\sl PRAAT, Python, Excel}
	\vspace*{-5pt}\begin{itemize}	\itemsep 0pt 
		\item Measured phonetic qualities of consultant-provided audio data using PRAAT.
		\item Performed corpus study of written Uyghur analyzing properties of backenss harmony.
	\end{itemize}
	\vspace*{0mm}
	
	{\textbf{Rogue-Like RPG}} \hspace*{5mm} {\sl Python, Curses} \\
	\vspace*{-5pt}\begin{itemize}	\itemsep 0pt
		\item Designed and implemented a game-engine for a terminal-based RPG using Python and the Python Curses module.
	\end{itemize}
	\vspace*{0mm}
	
	{\textbf{Web Scraper for Corpus Work}} \hspace*{5mm} {\sl Python, Scrapy, Tkinter}
	\vspace*{-5pt}\begin{itemize}	\itemsep 0pt 
		\item Constructed a web scraper using Python's Scrapy module to generate a corpus of written Uyghur.
		\item Implemented corpus data processing tools including regex search tool and Arabic/Latin transliterator.
	\end{itemize}
	\vspace*{0mm}
	
	{\textbf{Part of Speech Tagger}} \hspace*{5mm} {\sl Python, NLTK} \\
	\vspace*{-5pt}\begin{itemize}	\itemsep 0pt
		\item Developed a part of speech tagger for untagged corpora using Python Natural Language Tool-Kit.
		\item Model training was done using the open-source maximum entropy algorithm MegaM.
	\end{itemize}
	\vspace*{0mm}
	
		{\textbf{Dichotomous Key Tools (work in progress)}} \hspace*{5mm} {\sl Python} \\
	\vspace*{-5pt}\begin{itemize}	\itemsep 0pt
		\item Designed and implemented a code base to introduce useful functionalities to dichotomous keys.  These tools include interactive key traversal, key filtering based on arbitrary data (for example: geolocation, native status, etc), and nearest ancestor of two leaves. 
		\item Created key parser for plaintext from Jepson eFlora pages, with the goal of implementing webpage parsers for Jepson and other popular online floras.
		\item Goals for the project include creating a web interface and integrations with other online tools such including iNaturalist and Calflora.
	\end{itemize}
	\vspace*{0mm}
	
	{\textbf{Biodiversity Inventory of Under-documented area in Kern County}} \hspace*{5mm} \\
	\vspace*{-5pt}\begin{itemize}	\itemsep 0pt
		\item Conducted an ongoing, self-directed biodiversity inventory of an under-documented region along the South Fork of the Kern River Valley, roughly corresponding with the bounds of Onyx, CA.
		\item Recorded roughly 1000 observations using iNaturalist, including over 150 unique plant species.  Created and maintained a checklist page for the region to track likely and confirmed taxa.
		\item Documented several rare and uncommon species, as well as several species at the extreme edges of their known range.
		\item Relocated rare species based on the descriptions and geolocations provided in herbarium collections.
	\end{itemize}
	\vspace*{0mm}
	
	\header{Skills}
	\begin{tabular}{ l p{11.2cm} }
		Field Skills:          & Plant Identification, Specimen Collection, Seed Collection, Map \& Compass Navigation \\
		
		Tools / Environments:  & Git, UNIX, Windows, Jira, Jenkins, Docker, Kubernetes, Audacity, Excel, Google Workspace, Microsoft Office, \LaTeX
		\\
		Programming Languages: & Python, R Studio, Bash, SQL, C, C++
		\\
		Natural Languages:     & English \hfill (fluent, native) \newline Spanish, German \hfill (basic proficiency)
		\\
		\newline & Japanese \hfill (familiarity / elementary proficiency)
		\\
	\end{tabular}
	\vspace{2mm}
	
	
	%==== Education ====%
	\header{Education}
	\textbf{University of California, Los Angeles}\hfill Los Angeles, CA\\
	M.A. Linguistics \hfill Sep 2018 - Jun 2019\\
	\vspace{1mm}
	B.A. Linguistics and Computer Science \hfill Sep 2015 - Jun 2019\\
	\vspace{1mm}
	\vspace{1mm}
	
	\header{Coursework}
	Phonetics $\cdot$ Phonology $\cdot$ Syntax $\cdot$ Semantics $\cdot$ Computational Linguistics $\cdot$ Programming Languages $\cdot$ Formal Languages \& Automata Theory $\cdot$ Algorithms $\cdot$ Mathematical Structures in Language
	\vspace*{10mm}
	
\end{document}