\documentclass[]{article}
    \usepackage{fullpage}
    \usepackage{amsmath}
    \usepackage{amssymb}
    \usepackage{textcomp}
    \usepackage{hyperref}
    \usepackage[utf8]{inputenc}
    \usepackage[T1]{fontenc}
    \usepackage[margin=1in]{geometry}
    \textheight=10in
    \pagestyle{empty}
    \raggedright

%\renewcommand{\encodingdefault}{cg}
%\renewcommand{\rmdefault}{lgrcmr}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

% DEFINITIONS FOR RESUME %%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\area} [2] {
    \vspace*{-9pt}
    \begin{verse}
        \textbf{#1}   #2
    \end{verse}
}

\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hspace*{-18pt} \hrulefill \\
}

\newcommand{\header} [1] {
    {\hspace*{-18pt}\vspace*{6pt} \textsc{#1}}
    \vspace*{-6pt} \lineunder
}

\newcommand{\employer} [3] {
    { \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }
}

\newcommand{\contact} [3] {
    \vspace*{-10pt}
    \begin{center}
        {\Huge \scshape {#1}}\\
        #2 \\ #3
    \end{center}
    \vspace*{-8pt}
}

\newenvironment{achievements}{
    \begin{list}
        {$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}
    \end{list}
}

\newcommand{\schoolwithcourses} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
    \vspace*{5pt}
}

\newcommand{\school} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
}
% END RESUME DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%

    \begin{document}
\vspace*{-40pt}


%==== Profile ====% 
\vspace*{-10pt}
\begin{center}
	{\Huge \scshape {Tyler W. Carson}}\\
	$\ $San Jose, CA $\ \cdot\ $ tyler.w.carson@gmail.com $\ \cdot\ $ (909) 756-5942\\ linkedin.com/in/twcarson $\ \cdot\ $ github.com/yzgncx\\
\end{center}


%==== Work Experience ====%
\header{Work Experience}
\vspace{1mm}

\textbf{SoundHound, Inc.} \hfill Santa Clara, CA\\
\textit{Linguistic Engineer} \hfill Aug 2021 - Jan 2023\\
\vspace{-3mm}
\begin{itemize} \itemsep 0pt
	\item Created experimental and production acoustic models in several languages
	\item Lead meetings and coordinated presentations for a team of engineers and linguists.
	\item Worked in a small team to port a legacy repository from C to Python. 
\end{itemize}
\textit{Language Data Specialist} \hfill Mar 2020 - Aug 2021\\
\vspace{-3mm}
\begin{itemize} \itemsep 0pt
	\item Trained and debugged acoustic models and language models for automatic speech recognition. 
	\item Developed and iterated on a web tool for audio data collection written in Javascript \& HTML.
	\item Designed, set up, and maintained a MySQL database for cataloging text and audio data used in creating text to speech models.
\end{itemize}
\textit{English Data Intern} \hfill Aug 2019 - Mar 2020\\
\vspace{-3mm}
\begin{itemize} \itemsep 0pt
	\item Organized and lead scripting lessons and office hours for other interns and team members.
	\item Developed a collection of tools in Python for scraping and conditioning text data for use in a linguistic corpus.
\end{itemize}
\vspace{1mm}

\textbf{UCLA Linguistics} \hfill Los Angeles, CA\\
\textit{Undergraduate Researcher} \hfill Jul 2017 - Oct 2018\\
\vspace{-3mm}
\begin{itemize} \itemsep 0pt
	\item Conducted research on the relationship between surprisal and entropy reduction as measures of complexity for natural language.
	\item Developed software in OCaml for calculating the complexity of grammar in natural language sentences using concepts based in information-theory.
	\item Contributed code for calculating the entropy of a probabilistic formal grammar.
\end{itemize}

\header{Projects}
{\textbf{Analysis of Uyghur Vowel Harmony}} \hspace*{5mm} {\sl PRAAT, Python, Excel}
\vspace*{-5pt}\begin{itemize}	\itemsep 0pt 
	\item Measured phonetic qualities of consultant-provided audio data using PRAAT.
	\item Performed corpus study of written Uyghur analyzing properties of backenss harmony.
\end{itemize}
\vspace*{0mm}

{\textbf{Web Scraper for Corpus Work}} \hspace*{5mm} {\sl Python, Scrapy, Tkinter}
\vspace*{-5pt}\begin{itemize}	\itemsep 0pt 
	\item Built web scraper using Python's Scrapy module to generate a corpus of written Uyghur.
	\item Implemented corpus data processing tools including regex search tool and Arabic/Latin transliterator.
\end{itemize}
\vspace*{0mm}


{\textbf{Part of Speech Tagger}} \hspace*{5mm} {\sl Python, NLTK} \\
\vspace*{-5pt}\begin{itemize}	\itemsep 0pt
	\item Developed a part of speech tagger for untagged corpora using Python Natural Language Tool-Kit.
	\item Model training was done using the open-source maximum entropy algorithm MegaM.
\end{itemize}
\vspace*{0mm}
{\textbf{Text Based / Rogue-Like RPG}} \hspace*{5mm} {\sl C++, NCurses} \\
\vspace*{-5pt}\begin{itemize}	\itemsep 0pt
	\item Designed and implemented a game-engine for a terminal-based RPG using C++ and nCurses library.
\end{itemize}
\vspace*{0mm}

\header{Skills}
\begin{tabular}{ l p{11.2cm} }
	Tools / Environments:  & Git, UNIX, Jira, Jenkins, Docker, Kubernetes, Audacity, Emacs, Excel, \LaTeX
	\\
	Programming Languages: & Python, Bash, C, C++
	\\
	Natural Languages:     & English \hfill (fluent, native) \newline German \hfill (working proficiency)
	\\
\end{tabular}
\vspace{2mm}


%==== Education ====%
\header{Education}
\textbf{University of California, Los Angeles}\hfill Los Angeles, CA\\
M.A. Linguistics \hspace*{36mm} \textit{GPA: 4.00} \hfill Sep 2018 - Jun 2019\\
\vspace{1mm}
B.A. Linguistics and Computer Science \hspace*{1mm} \textit{GPA: 3.69} \hfill Sep 2015 - Jun 2019\\
\vspace{1mm}
\textbf{Crafton Hills College}\hfill Yucaipa, CA\\
A.A. Japanese Language and Culture \hspace*{3.8mm} \textit{GPA: 3.91} \hfill Sep 2013 - Jun 2015\\
\vspace{1mm}

\header{Coursework}
Phonetics $\cdot$ Phonology $\cdot$ Syntax $\cdot$ Semantics $\cdot$ Computational Linguistics $\cdot$ Programming Languages $\cdot$ Formal Languages \& Automata Theory $\cdot$ Algorithms $\cdot$ Mathematical Structures in Language
\vspace*{2mm}

\header{Honors and Awards}
\textbf{UCLA Linguistics Departmental Scholar}\\
Selected by UCLA Linguistics Faculty to complete 1-year master’s program. \hfill Spring 2018\\
\vspace*{1mm}
\textbf{UCLA Honors Summer Research Stipend} \hfill Summer 2018\\
\vspace*{1mm}
\textbf{UCLA College Honors Program}
\hfill Fall 2015 - Present\\
\vspace*{1mm}
\textbf{Crafton Hills College - Honors College Graduate}
\hfill Spring 2015\\
\vspace*{1mm}
\end{document}