\documentclass[]{article}
\usepackage{fullpage}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{textcomp}
\usepackage{hyperref}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[margin=1in]{geometry}
\textheight=10in
\pagestyle{empty}
\raggedright

%\renewcommand{\encodingdefault}{cg}
%\renewcommand{\rmdefault}{lgrcmr}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

% DEFINITIONS FOR RESUME %%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\area} [2] {
	\vspace*{-9pt}
	\begin{verse}
		\textbf{#1}   #2
	\end{verse}
}

\newcommand{\lineunder} {
	\vspace*{-8pt} \\
	\hspace*{-18pt} \hrulefill \\
}

\newcommand{\header} [1] {
	{\hspace*{-18pt}\vspace*{6pt} \textsc{#1}}
	\vspace*{-6pt} \lineunder
}

\newcommand{\employer} [3] {
	{ \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }
}

\newcommand{\contact} [3] {
	\vspace*{-10pt}
	\begin{center}
		{\Huge \scshape {#1}}\\
		#2 \\ #3
	\end{center}
	\vspace*{-8pt}
}

\newenvironment{achievements}{
	\begin{list}
		{$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}
	\end{list}
}

\newcommand{\schoolwithcourses} [4] {
	\textbf{#1} #2 $\bullet$ #3\\
	#4 \\
	\vspace*{5pt}
}

\newcommand{\school} [4] {
	\textbf{#1} #2 $\bullet$ #3\\
	#4 \\
}
% END RESUME DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
	\vspace*{-40pt}
	
	
	%==== Profile ====% 
	\vspace*{-10pt}
	\begin{center}
		{\Huge \scshape {Tyler W. Carson}}\\
		$\ $San Jose, CA $\ \cdot\ $ tyler.w.carson@gmail.com $\ \cdot\ $ (909) 756-5942\\ linkedin.com/in/twcarson $\ \cdot\ $ github.com/twcarson\\
	\end{center}
	
	
	%==== Work Experience ====%
	\header{Work Experience}
	\vspace{1mm}
	
	\textbf{Sensory, Inc.} \hfill Portland, OR (remote)\\
	\textit{Product Linguist} \hfill May 2023 - May 2025\\
	\vspace{-3mm}
	\begin{itemize} \itemsep 0pt
		\item Created, documented, and maintained internal software tools written in Python and Bash.
		\item Trained and tested artificial neural networks built for wake word and command recognition for major automotive and consumer electronics companies.
		\item Classified and categorized large language datasets for use in model training.
		\item Used research methods to find optimal model parameters and best practices for data curation.
		\item Balanced the work of several simultaneous projects with tight deadlines.
	\end{itemize}
	
	\textbf{SoundHound, Inc.} \hfill Santa Clara, CA\\
	\textit{Linguistic Engineer} \hfill Aug 2021 - Jan 2023\\
	\vspace{-3mm}
	\begin{itemize} \itemsep 0pt
		\item Created experimental and production acoustic models for several languages, often delivering models on tight time-frames.  Produced scripts to automate and streamline multi-step training processes.
		\item Lead meetings and coordinated presentations for a team of engineers and linguists.
		\item Worked in a small team to port a legacy repository from C to Python. 
	\end{itemize}
	\textit{Language Data Specialist} \hfill Mar 2020 - Aug 2021\\
	\vspace{-3mm}
	\begin{itemize} \itemsep 0pt
		\item Trained and debugged acoustic models and language models for automatic speech recognition.  
		\item Developed and maintained internal company web tool for audio data collection (Javascript, HTML) and audio corpus database for speech models (MySQL, Python).
	\end{itemize}
	\textit{English Data Intern} \hfill Aug 2019 - Mar 2020\\
	\vspace{-3mm}
	\begin{itemize} \itemsep 0pt
		\item Curated language datasets, annotated speech data in IPA and SAMPA, lead scripting lessons and office hours, and developed tools in Python for scraping and conditioning text data for use in a linguistic corpus.
	\end{itemize}
	\vspace{1mm}
	
	\textbf{UCLA Linguistics} \hfill Los Angeles, CA\\
	\textit{Undergraduate Researcher} \hfill Jul 2017 - Oct 2018\\
	\vspace{-3mm}
	\begin{itemize} \itemsep 0pt
		\item Developed software in OCaml for calculating the complexity of grammar in natural language sentences using concepts based in information-theory.
	\end{itemize}
	
	\header{Projects}
	{\textbf{Analysis of Uyghur Vowel Harmony}} \hspace*{5mm} {\sl PRAAT, Python, Excel}
	\vspace*{-5pt}\begin{itemize}	\itemsep 0pt 
		\item Measured phonetic qualities of consultant-provided audio data using PRAAT.
		\item Performed corpus study of written Uyghur analyzing properties of backenss harmony.
	\end{itemize}
	\vspace*{0mm}
	
	{\textbf{Web Scraper for Corpus Work}} \hspace*{5mm} {\sl Python, Scrapy, Tkinter}
	\vspace*{-5pt}\begin{itemize}	\itemsep 0pt 
		\item Constructed a web scraper using Python's Scrapy module to generate a corpus of written Uyghur.
		\item Implemented corpus data processing tools including regex search tool and Arabic/Latin transliterator.
	\end{itemize}
	\vspace*{0mm}
	
	{\textbf{Part of Speech Tagger}} \hspace*{5mm} {\sl Python, NLTK} \\
	\vspace*{-5pt}\begin{itemize}	\itemsep 0pt
		\item Developed a part of speech tagger for untagged corpora using Python Natural Language Tool-Kit.
		\item Model training used the open-source maximum entropy algorithm MegaM.
	\end{itemize}
	\vspace*{0mm}
	
	\header{Skills}
	\begin{tabular}{ l p{11.2cm} }
		Tools / Environments:  & Git, UNIX, Jira, Docker, Google Workspace, Audacity, Excel, \LaTeX
		\\
		Programming Languages: & Python, Bash, SQL, C, C++
		\\
		Natural Languages:     & English \hfill (fluent, native) \newline German, Spanish \hfill (basic proficiency)
		\\
	\end{tabular}
	\vspace{2mm}
	
	
	%==== Education ====%
	\header{Education}
	\textbf{University of California, Los Angeles}\hfill Los Angeles, CA\\
	M.A. Linguistics \hfill Sep 2018 - Jun 2019\\
	\vspace{1mm}
	B.A. Linguistics and Computer Science \hfill Sep 2015 - Jun 2019\\
	\vspace{1mm}
	\vspace{1mm}
	
	\header{Coursework}
	Phonetics $\cdot$ Phonology $\cdot$ Syntax $\cdot$ Semantics $\cdot$ Computational Linguistics $\cdot$ Programming Languages $\cdot$ Formal Languages \& Automata Theory $\cdot$ Algorithms $\cdot$ Mathematical Structures in Language
	\vspace*{10mm}
	
\end{document}